\section{Measurements}
\subsection{Adjustment of the Stokes' viscosity measurement device}
    \begin{enumerate}
        \item Make the plumb aiming at the center of the base by adjusting the knobs beneath the base.
        \item Turn on the two lasers and make the beams parallel and aim at the plumb line.
        \item Remove the plumb and place the flask with castor oil at the center of the base.
        \item Place the guiding pipe on the top of the device.
        \item Put a metal ball into it and check whether the ball can block the beams. If not, repeat. 
    \end{enumerate}
\subsection{Measurement of the (constant) velocity of a falling ball}
    \begin{enumerate}
        \item Measure the vertical distance $s$ between the two laser beams at least three times.
        \item Put a metal ball into the guiding pipe. Record the time it travels between the two beams for at least six times.
    \end{enumerate}
\subsection{Measurement of the ball density $\rho_2$}
    \begin{enumerate}
        \item Use electronic scales to measure the mass of 40 metal balls. Calculate the average.
        \item Use a micrometer to measure the diameter of the ball for ten times.
        \item Calculate the density $\rho_2$.
    \end{enumerate}
\subsection{Other measurements}
    \begin{enumerate}
        \item Read the density of the castor oil $\rho_1$ by a densimeter.
        \item Measure the inner diameter of the flask for six times.
        \item Read the temperature from the thermometer.
    \end{enumerate}    
\subsection{Calculation of the value of viscosity coefficient}
    Calculate $\eta$ using Eq.\ref{eta2}.
