\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\geometry{left=1.0in, top=0.5in, left=1.0in, right=1.0in}
\begin{document}
    \begin{center}
        \Huge{\textbf{Minutes of Group 8}}\\
        \vspace{1ex}
        \begin{normalsize}
            Sijun Zhang 516370910155\\
            Yunping Chou 516370910156\\
            Tianyi Ge 516370910168\\
            Fubo Qi 516370910175\\
        \end{normalsize}        
    \end{center}
    \section{Progress:}
    Because P1 is just finished and we had the mid-term on Thursday, this week is
    mainly focus on the exam and the oncoming P2 proposal. We discussed our origin ideal, the  smart 
    bicycle lock, and and realize that our project is a little bit easy for the main function is integrated.
    We try to figure out if is there any extension we can make to make our project more useful and useful. 
    Make a rough draft of our proposal.
    \section{Problems:}
    \begin{itemize}
        \item The time left for P2 is limited, we are not sure whether we can deal with
        the additional function well. 
        \item Still, we are uncertain about our main toptic of our proposal.
        \item Worries about the technologic problems, we are not prepared enough.
    \end{itemize}
    \section{Conflicts:}
        In the discussion, we agree on that we need add some new features to our project,
        while we can not reach an agreement what to add and how considering there are just
        less than a month left. Qi tries to integrate a GPS navigation to the system while 
        he is unable to persuade others that this function can be reached within a month.
\end{document}
