\section{Conclusion and Discussion}


In this lab, we have studied the harmonic oscillation 
and the relations between $T$, $M$, $k$ and $v_{\max}$. 
Now we analyze the results.


\subsection{Spring Constant}


\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
spring 1 & 2.3311 $\pm$ 0.013[N/m] \\ \hline
spring 2 & 2.3206 $\pm$ 0.0105[N/m] \\ \hline
spring series & 1.165 $\pm$ 0.0380[N/m]  \\ \hline
\end{tabular}
\caption{The spring constant}
\end{table}


For the relative uncertainty are all very small,
the experiment in this part is very accurate.

By theory, we can calculate $k_3$, i.e. the $k$ of the spring serial by 
$$ k_{3,theory} = \frac{k_1 \cdot k_2 }{k_1 + k_2} =  1.1629 $$ 

Compared with $k_3 = 1.1649$  from the experiment,
$$ u_{k_{3,theory},k_3} = \frac{1.1649 - 1.1629}{1.1629} \cdot 100 \%  = 0.17 \% $$ 
The theory data is close to the experiment data.

The accurate experimental results prove that Hooke’s Law.



\subsection{Relation between the period $T$ and the mass $M$}

From curve fitting, we find that $T^2$  is linearly dependent with $M$
The slope is shown below:

\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
horizontal  &  8.3233 $\pm$  0.2235 [s2/kg] \\ \hline
incline 1   &  8.4380 $\pm$  0.0500 [s2/kg] \\ \hline
incline 2   &  8.3467 $\pm$  0.2185 [s2/kg] \\ \hline
\end{tabular}
\caption{Slope}
\end{table}

We find the slopes of three cases are very close to each other, 
so the ratio between $T^2$ and $M$  are independent of the incline degree of the air track.
We see all the relative errors are very small,
thus the result in this part is very accurate.

\subsection{The relation between $T$ and  $A$}

From the failed fitting curve, we find there is no clear linear relation between $T$ and $A$.
Thus, we can conclude that $T$ is independent of $A$.


\subsection{Relation between $ v_{\max}$ and $A$}

From the fitting curve we find that  $v_{\max}^2$ and $A^2$ is linearly dependent.
And 
$$ k =   23.6964 \pm 0.3300  $$
$$ u_{k,r} = 1.39 \% $$

The relative uncertainty of the experimental ratio is $1.39\%$, 
which is moderate. 
Thus the result is quite precise.
Still, $v_{\max}^2$ is more easily affected by the friction force, so the relative uncertainty is quite large. 
